Error Reporting Parsers: a Monad Transformer Approach

### 2013-06-21 article.tex
Parser article:  start position reporting section

... new code ...

>>>>

Knowing that a close-parenthesis is missing, somewhere deep inside a nested mess
of forms isn't very helpful -- you also want to know where it happened.  Let's 
add that to our parser.

\subsection{Parser type}

Once again, we extend the monad transformer stack with another layer -- a second
state layer, in which the line and column position will be kept as simple Ints.
The error type is also extended to include a position as well as a message:
\begin{verbatim}
type Pos = (Int, Int)
type Err = (String, Pos)

type Parser t a = StateT [t] (StateT Pos (MaybeT (Either Err))) a 
\end{verbatim}

And \verb+runParser+ is extended to support the new stack; it assumes we always
start parsing at line 1, column 1:
\begin{verbatim}
runParser :: Parser t a -> [t] -> Either Err (Maybe ((a, [t]), Pos))
runParser p ts = runMaybeT $ runStateT (runStateT p ts) (1, 1)
\end{verbatim}

Now that we have two separate state layers, we need to be sure not to mix them 
up (fortunately, Haskell's type system will helpfully complain if I mess up);
the \verb+lift+ method of the \verb+MonadTrans+ type class allows us to access
the position state:
\begin{verbatim}
getState :: Parser Char Pos
getState = lift get

putState :: Pos -> Parser Char ()
putState = lift . put

updateState :: (Pos -> Pos) -> Parser Char ()
updateState f = getState >>= (putState . f)
\end{verbatim}

\subsection{}
